|

### 2021-08-04 paper/dcpo_demsupport.Rmd
removing the overstatement in the memo

```{r num-pointAJPS, results='asis', eval=TRUE}
tb_result_cls <- purrr::map(result_clsAJPS, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)})

@@

modelsummary(tb_result_cls,  
             statistic = "conf.int",
             coef_map = names_coef, 
             output = "latex", 
             title = "Original") %>%

  kableExtra::kable_styling(font_size = 8) %>% 
  kableExtra::kable_styling(latex_options = "HOLD_position")
```

```{r num-pureAJPS, results='asis', eval=TRUE}
tb_result_pureAJPS <- purrr::map(result_pureAJPS, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)})

@@

modelsummary(tb_result_pureAJPS, 
             statistic = "conf.int",
             coef_map = names_coef, 
             output = "latex", 
             title = "W. Uncertainty") %>% 
  kableExtra::kable_styling(latex_options = "HOLD_position")
```

```{r num-expAJPS, results='asis', eval=TRUE}
tb_result_expAJPS <- purrr::map(result_expAJPS, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)})

@@

modelsummary(tb_result_expAJPS, 
             statistic = "conf.int",
             coef_map = names_coef, 
             output = "latex", 
             title = "W. Uncertainty and Expanded Data") %>% 
  kableExtra::kable_styling(latex_options = "HOLD_position")
```

@@

```{r num-pointAPSR, results='asis', eval=TRUE}
tb_result_clsAPSR <- map(result_clsAPSR, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)}) %>% 
  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]

names(tb_result_clsAPSR) <- c("ECM", "ECM-Regime", "FD", "FD-Regime","ECM Corrup", "ECM Corrup-Regime", "FD Corrup", "FD Corrup-Regime")

modelsummary(tb_result_clsAPSR, 
             stars = TRUE,
             coef_map = names_coef, 
             output = "latex", 
             title = "Original") %>% 
  kableExtra::kable_styling(font_size = 7) %>% 
  kableExtra::kable_styling(latex_options = "HOLD_position")
```

@@

```{r num-pureAPSR, results='asis', eval=TRUE}
tb_result_pureAPSR <- purrr:::map(result_pureAPSR, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)}) %>% 
  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]

names(tb_result_pureAPSR) <- c("ECM", "ECM-Regime", "FD", "FD-Regime","ECM Corrup", "ECM Corrup-Regime", "FD Corrup", "FD Corrup-Regime")

modelsummary(tb_result_pureAPSR, 
             statistic = "conf.int",
             coef_map = names_coef, 
             output = "latex", 
             title = "W. Uncertainty") %>% 
  kableExtra::kable_styling(font_size = 7) %>% 
  kableExtra::kable_styling(latex_options = "HOLD_position")
```

@@

```{r num-expAPSR, results='asis', eval=TRUE}
tb_result_expAPSR <- map(result_expAPSR, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)}) %>% 
  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]

names(tb_result_expAPSR) <- c("ECM", "ECM-Regime", "FD", "FD-Regime","ECM Corrup", "ECM Corrup-Regime", "FD Corrup", "FD Corrup-Regime")

modelsummary(tb_result_expAPSR, 
             statistic = "conf.int",
             coef_map = names_coef, 
             output = "latex", 
             title = "W. Uncertainty and Expanded Data") %>% 
  kableExtra::kable_styling(font_size = 7) %>% 
  kableExtra::kable_styling(latex_options = "HOLD_position")
```

>>>>

```{r num-pointAJPS, results='asis', eval=TRUE}
tb_result_cls <- purrr::map(result_clsAJPS, ~ {
    names(.) <- c("tidy", "glance")
    class(.) <- "modelsummary_list"
    return(.)
})

@@

modelsummary(tb_result_cls,
             # statistic = "conf.int",
             coef_map = names_coef,
             output = "latex",
             title = "Original") %>%
    kableExtra::kable_styling(font_size = 8) %>%
    kableExtra::kable_styling(latex_options = "HOLD_position")
```

```{r num-pureAJPS, results='asis', eval=TRUE}
tb_result_pureAJPS <- purrr::map(result_pureAJPS, ~ {
    .[[1]] <- rename(.[[1]], std.error = se)
    names(.) <- c("tidy", "glance")
    class(.) <- "modelsummary_list"
    return(.)
})

@@

modelsummary(
    tb_result_pureAJPS,
    # statistic = "conf.int",
    coef_map = names_coef,
    output = "latex",
    title = "W. Uncertainty"
) %>%
    kableExtra::kable_styling(latex_options = "HOLD_position")
```

```{r num-expAJPS, results='asis', eval=TRUE}
tb_result_expAJPS <- purrr::map(result_expAJPS, ~ {
    .[[1]] <- rename(.[[1]], std.error = se)
    names(.) <- c("tidy", "glance")
    class(.) <- "modelsummary_list"
    return(.)
})

@@

modelsummary(
    tb_result_expAJPS,
    # statistic = "conf.int",
    coef_map = names_coef,
    output = "latex",
    title = "W. Uncertainty and Expanded Data"
) %>%
    kableExtra::kable_styling(latex_options = "HOLD_position")
```

@@

```{r num-pointAPSR, results='asis', eval=TRUE}
tb_result_clsAPSR <- map(result_clsAPSR, ~ {
    names(.) <- c("tidy", "glance")
    class(.) <- "modelsummary_list"
    return(.)
}) %>%
    .[c(
        "pooled1",
        "pooled-regime1",
        "fd1",
        "fd-regime1",
        "pooled2",
        "pooled-regime2",
        "fd2",
        "fd-regime2"
    )]

names(tb_result_clsAPSR) <-
    c(
        "ECM",
        "ECM-Regime",
        "FD",
        "FD-Regime",
        "ECM Corrup",
        "ECM Corrup-Regime",
        "FD Corrup",
        "FD Corrup-Regime"
    )

modelsummary(
    tb_result_clsAPSR,
    # statistic = "conf.int",
    coef_map = names_coef,
    output = "latex",
    title = "Original"
) %>%
    kableExtra::kable_styling(font_size = 7) %>%
    kableExtra::kable_styling(latex_options = "HOLD_position")
```

@@

```{r num-pureAPSR, results='asis', eval=TRUE}
tb_result_pureAPSR <- purrr:::map(result_pureAPSR, ~ {
    .[[1]] <- rename(.[[1]], std.error = se)
    names(.) <- c("tidy", "glance")
    class(.) <- "modelsummary_list"
    return(.)
}) %>%
    .[c(
        "pooled1",
        "pooled-regime1",
        "fd1",
        "fd-regime1",
        "pooled2",
        "pooled-regime2",
        "fd2",
        "fd-regime2"
    )]

names(tb_result_pureAPSR) <-
    c(
        "ECM",
        "ECM-Regime",
        "FD",
        "FD-Regime",
        "ECM Corrup",
        "ECM Corrup-Regime",
        "FD Corrup",
        "FD Corrup-Regime"
    )

modelsummary(
    tb_result_pureAPSR,
    # statistic = "conf.int",
    coef_map = names_coef,
    output = "latex",
    title = "W. Uncertainty"
) %>%
    kableExtra::kable_styling(font_size = 7) %>%
    kableExtra::kable_styling(latex_options = "HOLD_position")
```

@@

```{r num-expAPSR, results='asis', eval=TRUE}
tb_result_expAPSR <- map(result_expAPSR, ~ {
    .[[1]] <- rename(.[[1]], std.error = se)
    names(.) <- c("tidy", "glance")
    class(.) <- "modelsummary_list"
    return(.)
}) %>%
    .[c(
        "pooled1",
        "pooled-regime1",
        "fd1",
        "fd-regime1",
        "pooled2",
        "pooled-regime2",
        "fd2",
        "fd-regime2"
    )]

names(tb_result_expAPSR) <-
    c(
        "ECM",
        "ECM-Regime",
        "FD",
        "FD-Regime",
        "ECM Corrup",
        "ECM Corrup-Regime",
        "FD Corrup",
        "FD Corrup-Regime"
    )

modelsummary(
    tb_result_expAPSR,
    # statistic = "conf.int",
    coef_map = names_coef,
    output = "latex",
    title = "W. Uncertainty and Expanded Data"
) %>%
    kableExtra::kable_styling(font_size = 7) %>%
    kableExtra::kable_styling(latex_options = "HOLD_position")
```

### 2021-08-04 paper/memo/memo.Rmd
removing the overstatement in the memo

---
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: ../svm-latex-ms2.tex
title: |
    | Democracy, Public Support, and Measurement Uncertainty
    | Memo to Reviewers
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
spacing: double
bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), ".bib$", recursive = TRUE))`}
biblio-style: apsr
citecolor: black
linkcolor: black
endnote: no
header-includes:
      - \usepackage{array}
      - \usepackage{caption}
      - \usepackage{graphicx}
      - \usepackage{siunitx}
      - \usepackage{colortbl}
      - \usepackage{multirow}
      - \usepackage{hhline}
      - \usepackage{calc}
      - \usepackage{tabularx}
      - \usepackage{threeparttable}
      - \usepackage{wrapfig}
---

@@

## Response
Regarding Reviewer 1's request on replicating all specifications in the original two studies, we added alternate specifications on the relationship between public support and democracy, including GMM models, First Different Models, and sample split.
Results do not change in all these models, presented on Page xxx, Figure xxx, and xxx in SI. 
As the editor suggested, this letter should focus on the core point: the relationship between public support and democracy. We do not replicate specifications on other relationships.

*Need to add APSR models or more description on full models*

@@

## Response
Thanks to the editor's suggestions, we agree that we should present and assess the effect of intermediate modification in an incremental way.
To do this, in the revised manuscript, we replicated Claassen's measure for public democratic support by applying his measurement Model5 to his original data file and used the posterior distribution of the public support estimates to incorporate uncertainty. 
Then, we added more survey data to improve source data quality and applied Model5 to this expanded data set, still keeping the full posterior distribution of estimates.
In this way, we isolate the effects of measurement uncertainty and more data. 
In the APSR analyses, it is uncertainty that accounts for the disappearing significance of public support.

@@

## Response
It is a misunderstanding that incorporating uncertainty only changes standard error.
First, incorporating uncertainty might or might not cause the changes of standard error.
For example, standard errors did not change after accounting for uncertainty in [@caughey2018] but became smaller in [@Treier2008].
Second, the propagation of uncertainty can either attenuate or magnify the magnitude of estimated effects.
*We can cite more lit if necessary*. 
To avoid confusion, we only focus on uncertainty in this revised version.

@@

## Response
We might need to review the functions added in SI.

>>>>

---
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: xelatex
    template: ../svm-latex-ms2.tex
title: |
    | Democracy, Public Support, and Measurement Uncertainty
    | Memo to Reviewers
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
spacing: double
bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), ".bib$", recursive = TRUE))`}
biblio-style: apsr
citecolor: black
linkcolor: black
endnote: no
header-includes:
      - \usepackage{array}
      - \usepackage{caption}
      - \usepackage{graphicx}
      - \usepackage{siunitx}
      - \usepackage{colortbl}
      - \usepackage{multirow}
      - \usepackage{hhline}
      - \usepackage{calc}
      - \usepackage{tabularx}
      - \usepackage{threeparttable}
      - \usepackage{wrapfig}
---

@@

## Response
Regarding Reviewer 1's request on replicating all specifications in the original two studies, we added alternate specifications on the relationship between public support and democracy, including GMM models, First Different Models, and sample split.
See Page xxx, Figure xxx, and xxx in SI.

@@

## Response
Thanks to the editor's suggestions, we agree that we should present and assess the effect of intermediate modification in an incremental way.
To do this, in the revised manuscript, we replicated Claassen's measure for public democratic support by applying his measurement Model5 to his original data file and used the posterior distribution of the public support estimates to incorporate uncertainty. 
Then, we added more survey data to improve source data quality and applied Model5 to this expanded data set, still keeping the full posterior distribution of estimates.
In this way, we isolate the effects of measurement uncertainty and more data. 
In replications for both AJPS and APSR analyses, it is uncertainty that accounts for the disappearing significance of public support and changes in democracy. 
In Supplementatry material, we explained the methodology for addressing measurement uncerainty in this study and compared Rubin's Rules and Method of Composition.
Both methods yield the similar results in significant, though they address measurement errors in different angles.

In terms of disappearing relationships between public support and democracy and the change in mood and the change in democracy, we have discussed theoretical reasons in our main text. 
It is possbile that the relationship is negligible, because the incorporation of measurement error swamping the significant effects of democracy in a strong relationship is rare [@Treier2008].

In addition to potential methodological explanations we have discussed, another potential reason is the over-time smoothing induced by the random-walk prior thanks to Reviwer 2's suggestion.
At aggregated level, country-year data is super sparse. 
Even in our expanded data, xx data is missing, compared to xxx missing in original data.
The sparse of raw data and the simple dynamic linear model used in measurement model to capture dynamic effect might make priors dominate in smoothing over-time changes. 
However, in our revised manuscript, we only used Claassen's Model 5 to estimate public support using corrected original data and expanded data, seperately.
Since our expanded data added xxx country-year, the estimates from the expanded data should be influenced less by priors than original data by inputing more data. 
Still, the coefficient estimates from expanded data are indistinguishable from zero though with narrower confident interval.
Therefore, it is the incorporation of uncertainty that changes the coefficient estimates in magnitude and significant.

@@

## Response
It is a misunderstanding that incorporating uncertainty only changes standard error.
First, incorporating uncertainty might or might not cause the changes of standard error.
For example, standard errors did not change after accounting for uncertainty in [@caughey2018] but became smaller in [@Treier2008].
Second, the propagation of uncertainty can either attenuate or magnify the magnitude of estimated effects.
To avoid confusion, we only focus on uncertainty in this revised version.

@@

## Response
In SI, we discussed methodology used in this article to address measurement errors, Rubin's Rules and MOC.
We compared these two methods by introducing their fomulas and equations and highlighing their different approaches. 
As results show, though they have different approaches, the results from two methods are similar with each other.
